JLyrics \titlenote{Submitted as the final project for CS 410 Summer 2014.}

### 2014-08-02 report/paper.tex
Added a screenshot and completed the piapro section.

Due to the sheer number of songs to crawl, it became necessary to distribute the processing over a number of computers. Another issue was that EWS lacks the required libraries to compile this code or even run the executable. As a result, a simplification needed to be made. This time, the crawler simply took the html files, so that they could all be processed on a machine with the required library files. In short, the original crawler was split into two parts. As a result, the following scheme was used: (Note: Actual number of docs ended up being 141,303, but due to the site being updated, there were duplicate links.)

@@

>>>>

Due to the sheer number of songs to crawl, it became necessary to distribute the processing over a number of computers. Another issue was that EWS lacks the required libraries to compile this code or even run the executable. As a result, a simplification needed to be made. This time, the crawler simply took the html files, so that they could all be processed on a machine with the required library files. In short, the original crawler was split into two parts. As a result, the following scheme was used: (Note: Ideally, the number of links would have been 141,303, but due to the site being updated, there were duplicate links.)

@@

Unfortunately, because the pre-processed HTML files are considerably larger than the post-processed ones, the EWS machines ran out of space. Due to this unforseen occurrence, we didn't think to save space by clearing out unnecessary files, and only around 1GB's worth of HTML files could be downloaded. In reality, the number of documents indexed only ended up being 127,223 instead of an estimated 154,000.
